Distributions

### 2021-12-16 Ch2_distributions/Ch2_Figures.Rmd
Figure for curves is not working and I don't know that it is worth it

>>>>

data <- cp.boot.fits

  data %>% 
    filter(dBIC == 0, dist == "gamma", param == "shape") -> gam.shape

  data %>% 
    filter(dBIC == 0, dist == "gamma", param == "shape") -> gam.scale

  data %>% 
    filter(dBIC == 0, dist == "lnorm", param == "meanlog") -> ln.mean

    data %>% 
    filter(dBIC == 0, dist == "lnorm", param == "sdlog") -> ln.sd

  data %>% 
    filter(dBIC == 0, dist == "weibull", param == "shape") -> wei.shape

  data %>% 
    filter(dBIC == 0, dist == "weibull", param == "scale") -> wei.scale

  gamma.curves <- purrr::map(seq(1:nrow(gam.shape)), function(y)
  stat_function(fun = dlnorm, args = list(shape = gam.shape$estimate[y],
                                          scale = gam.scale$estimate[y]),
                                          color = cols.fig2[1]))

  lnorm.curves <- purrr::map(seq(1:nrow(ln.mean)), function(y)
  stat_function(fun = dlnorm, args = list(meanlog = ln.mean$estimate[y],
                                          sdlog = ln.sd$estimate[y]),
                                          color = cols.fig2[2]))

  weibull.curves <- purrr::map(seq(1:nrow(wei.scale)), function(y)
  stat_function(fun = dlnorm, args = list(scale = wei.scale$estimate[y],
                                          shape = wei.shape$estimate[y]),
                                          color = cols.fig2[3]))

  reg_fits_info %>% 
  filter(., model == "CP", dBIC == 0) -> b

  ggplot() +
    gamma.curves +
    # stat_function(fun = dlnorm, args = list(meanlog = b$estimate[1],
    #                                         sdlog = b$estimate[2])) +
    lims(x = c(0, 200)) +
    theme_classic() -> curves1

    ggplot() +
    lnorm.curves +
    # stat_function(fun = dlnorm, args = list(meanlog = b$estimate[1],
    #                                         sdlog = b$estimate[2])) +
    lims(x = c(0, 200)) +
    theme_classic() -> curves2

    ggplot() +
    weibull.curves +
    # stat_function(fun = dlnorm, args = list(meanlog = b$estimate[1],
    #                                         sdlog = b$estimate[2])) +
    lims(x = c(0, 200)) +
    theme_classic() -> curves3

    plot_grid(curves1, curves2, curves3, nrow = 3)
